Different forms of uncertainty differently affect the evolution of social learning

### 2022-10-18 ms.tex
updated figures and added affiliations

\usepackage{xcolor}
% \renewcommand{\linenumberfont}{\small\color{gray}}

@@

\author{{}}

\begin{document}
\maketitle

>>>>

\usepackage{authblk}
\renewcommand\Affilfont{\small}

\author[1,*]{Matthew A. Turner}
\author[2,3]{Cristina Moya}
\author[4,5,6]{Paul E. Smaldino}
\author[1,6]{James Holland Jones}

\affil[1]{Department of Earth System Science, Stanford University, Stanford, CA 94305 USA}
\affil[2]{Department of Anthropology, University of California at Davis, Davis, CA 95616 USA}
\affil[3]{Centre for Culture and Evolution, Brunel University London, Uxbridge, UB8 3PH UK}
\affil[4]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
\affil[5]{Santa Fe Institute, Santa Fe, NM 87501 USA}
\affil[6]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
\affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
\usepackage{xcolor}
% \renewcommand{\linenumberfont}{\small\color{gray}}

@@

\begin{document}
\maketitle
\clearpage
